\subsection{Abbreviations}
    \begin{description}
        \item[API] Application programming interface; a software interface for
        interoperability between applications.
        \item[CDR] Common data representation. A transfer syntax for exchanging information
        between systems, which is independent from the systems' choice
        of programming language.
        \item[CSV] Comma separated values; a plain-text data exchange format for homogenous
        data.
        \item[ORM] Object-relational-mapper; a software library for persisting objects
        in object-oriented languages in a relational database.
        \item[ODM] Object-document-mapper; a software library for persisting objects
        in object-oriented languages in a document-based database.
        \item[xAPI] Experience API, formerly TinCan API; an API specification for
        exchanging data about learning activities.
        \item[REST] Representational state transfer; a paradigm for API design.
        \item[JSON] JavaScript object notation; a plain-text data exchange format.
        \item[ACID] Atomicity, consistency, isolation, durability; a set of properties
        for database transaction, aiming to guarantee data validity in the event of failure.
        \item[SQL] Structured query language; a language for interfacing with database systems.
        \item[TLA] Trusted learning analytics; a big data storage and analysis infrastructure
        developed at Prof. H. Drachsler's work group.
        \item[LRS] Learning record store; a big data store for xAPI statements.
        \item[LTI] Learning technologies interoperability; a protocol for integrating third-party
        services with an LMS.
        \item[LMS] Learning management system; a content management system specifically
        designed for learning environments.
        \item[CAS] Central authentication service; the user authentication service provided
        by the HRZ at Goethe University.
        \item[HRZ] Hochschulrechenzentrum; Data center and IT service provider at Goethe University.
    \end{description}